A Systematic Literature Review on Extensions to Role Based Access Control

### 2013-02-27 paper/sections/intro.tex
Adds research questions to introductionwq

\textit{The goal of this work is to provide practitioners an assessment of the state of extended models of RBAC and researchers with insights into the lack of robust evaluation of RBAC extension models.}

>>>>

\textit{The goal of this work is to provide practitioners an assessment of the state of extended models of RBAC and researchers with insights into the lack of robust evaluation of RBAC extension models.} With respect to our goal, the authors addressed the following research questions:

\begin{itemize}
\item What categorizations exist within extensions to RBAC?
\item What are the motivations behind extensions to RBAC?
\item Do the extensions to RBAC have corresponding implementations?
\item How are extensions to RBAC evaluated theoritically and in practice?
\item What domains have extensions to RBAC been created for?
\item What commonalities or generalizations exist across all categorizations?
\end{itemize}
